Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-20 paper/paper.qmd
plots and stats

this is all i want in main:
---
title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
subtitle: "Exploratory Data Analysis (EDA)"
author: 
  - Navya Hooda
  - Mohammed Yusuf Shaikh
  - Shivank Goel
  - Vanshika Vanshika
  - Jena Shah
date: today
date-format: long
number-sections: true
format: pdf
bibliography: references.bib
---

# install.packages(c("tidyverse", "janitor", "here", "lubridate", "arrow", "dplyr", 
#   "knitr", "performance", "kableExtra", #"ggpubr"))

@@

@@

```{r}

#| label: fig-boxplot-game-scores
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Memory Game Scores by Drug Type and Dosage Level"

>>>>

---
title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
subtitle: "Exploratory Data Analysis (EDA)"
author: 
  - Navya Hooda
  - Mohammed Yusuf Shaikh
  - Shivank Goel
  - Vanshika Vanshika
  - Jena Shah
date: today
date-format: long
number-sections: true
format: pdf
bibliography: references.bib
---

@@

colnames(summary_table) <- c("Statistic", "Memory Game Score", "Memory Cards Score")

@@

```{r}
#| label: fig-boxplot-game-scores
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Memory Game Scores by Drug Type and Dosage Level"
